### 2024-11-26 paper/paper.qmd
added some graphs in paper.qmd

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(kableExtra)

data <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))
print(data)
```

# Introduction

```{r}
#| label: cleaned_dataset-preview
#| fig-cap: "Preview of the Cleaned Dataset"
#| echo: false

# TABLE 1: CLEANED DATASET
data %>% head(5)
```

```{r}
#| label: summary_statistic_cleaned_dataset
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

data %>% 
  select(-c(title, author)) %>% 
  summary(rated-high) %>% 
  kable(booktabs = TRUE, linesep = "") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

```

# Data {#sec-data}

```{r}
#| label: summary_statistic_cleaned_dataset
#| fig-cap: "Summary Statistic of the Cleaned Dataset"
#| echo: false

ggplot(data, aes(x = publish_year, y = rating)) +
  geom_point()
```

\newpage

# References

### 2024-11-26 paper/paper.qmd
fixed clean_data.R to save parquet file instead of csv

@@
 
-ggplot(data, aes(x = publish_year, y = rating)) +
+data2 <- data %>% filter(rating > 4 )
+
+ggplot(data2, aes(x = publish_year, y = rating)) +
+  geom_point() +
+  theme_minimal()
+
+ggplot(data2, aes(x = rating_count, y = rating)) +
   geom_point()
+
+ggplot(data2, aes(x = pages, y = rating)) +
+  geom_point()
+
+ggplot(data2, aes(y = cover)) + 
+  geom_bar() +
+  theme_minimal()
+
 ```

### 2024-11-26 scripts/03-clean_data.R

@@ -10,6 +10,8 @@
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
+library(readr)
+library(arrow)
 
 #### Clean data ####
 data <- read.delim("data/01-raw_data/childrens-books.txt", header = TRUE, sep = "\t")
@@ -21,5 +23,5 @@ data$"rated_high" <- ifelse(data$rating > 4, 1, 0)
 # drop unnecessary columns 
 data <- data %>% select(-c(isbn, original_publish_year))
 
-#### Save data ####
-write_csv(data, "data/02-analysis_data/analysis_data.csv") 
+#### Save data in parquet file ####
+write_parquet(data, "data/02-analysis_data/analysis_data.parquet") 

### 2024-11-26 paper/paper.qmd
renamed folders

@@
 
-data <- read.csv(here::here("data/02-analysis_data/analysis_data.csv"))
+data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
 print(data)
@@
 
-ggplot(data2, aes(x = rating_count, y = rating)) +
-  geom_point()
+ggplot(data2, aes(x = rating, y = rating_count)) +
+  geom_point() +
+  geom_smooth( se =FALSE, color = "red", size = 1)
 
-ggplot(data2, aes(x = pages, y = rating)) +
-  geom_point()
+ggplot(data2, aes(x = rating, y = pages)) +
+  geom_point() +
+  geom_smooth(method = "lm", se = FALSE, color = 'red', size = 1)
 
@@
   geom_bar() +
+  theme_minimal()
+
+avg_pages <- aggregate(pages ~ rated_high, data = data, FUN = mean, na.rm = TRUE)
+
+ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
+  geom_bar(stat = "identity") +
+  labs(
+    title = "Average Pages by High Rated",
+    x = "High Rated (1 = Yes, 0 = No)",
+    y = "Average Pages",
+    fill = "High Rated"
+  ) +
+  theme_minimal()
+
+cover_counts <- data %>%
+  group_by(rated_high, cover) %>%
+  summarise(count = n()) %>%
+  ungroup()
+
+ggplot(cover_counts, aes(x = cover, y = count, fill = cover)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~ rated_high) +
+  labs(title = "Count of Hardcover and Paperback by Rated High",
+       x = "Cover Type",
+       y = "Count") +
   theme_minimal()

### 2024-11-26 scripts/03-clean_data.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the children'sbook data
+# Author: Hyunje Park 
+# Date: November 26, 2024
+# Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
 
 #### Workspace setup ####
 library(tidyverse)
@@ -14,7 +13,7 @@ library(readr)
 library(arrow)
 
 #### Clean data ####
-data <- read.delim("data/01-raw_data/childrens-books.txt", header = TRUE, sep = "\t")
+data <- read.delim("data/raw_data/childrens-books.txt", header = TRUE, sep = "\t")
 print(data)
 
 # make a new column that determines if a book is high rated 
@@ -24,4 +23,4 @@ data$"rated_high" <- ifelse(data$rating > 4, 1, 0)
 data <- data %>% select(-c(isbn, original_publish_year))
 
 #### Save data in parquet file ####
-write_parquet(data, "data/02-analysis_data/analysis_data.parquet") 
+write_parquet(data, "data/analysis_data/analysis_data.parquet") 

### 2024-11-26 paper/paper.qmd
added all the visualizations in paper.qmd

@@
 library(kableExtra)
+library(arrow)
+library(readr)
+library(rstanarm)
+library(modelsummary)
 
-data <- read.csv(here::here("data/analysis_data/analysis_data.csv"))
+data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 print(data)
@@
 data %>% 
-  select(-c(title, author)) %>% 
+  select(-c(title)) %>% 
   summary(rated-high) %>% 
@@
 \newpage
+```{r}
+#| label: summary_statistic_cleaned_dataset
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
 
+model_file <- readRDS(file = here::here("models/model.rds"))
+
+modelsummary(
+  list (
+    "Book is High-Rated" = model_file
+  ),
+  statistic = "mad"
+)
+
+```
+
+```{r}
+#| label: summary_statistic_cleaned_dataset
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+
+pp_check(model_file) +
+  theme(legend.position = "bottom")
+
+```
+
+```{r}
+#| label: summary_statistic_cleaned_dataset
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+
+posterior_vs_prior(model_file, size = 0.3) +
+   theme_minimal() +
+   theme(legend.position = "bottom") +
+   theme(axis.text.x=element_text(hjust=1, vjust=0.5),
+         text=element_text(size=8)) +
+   coord_flip()
+
+```
+
+```{r}
+#| label: summary_statistic_cleaned_dataset
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+#| fig-subcap: ["Intercept", "pages", "rating_count", "publish_year", "coverEbook", "coverKindle", "coverBoard", "coverHardcover", "coverPaperback"]
+#| layout-ncol: 3
+
+plot(model_file, "trace", "(Intercept)")
+plot(model_file, "trace", "pages")
+plot(model_file, "trace", "rating_count")
+plot(model_file, "trace", "publish_year")
+plot(model_file, "trace", "coverEbook")
+plot(model_file, "trace", "coverKindle Edition")
+plot(model_file, "trace", "coverBoard Book")
+plot(model_file, "trace", "coverHardcover")
+plot(model_file, "trace", "coverPaperback")
+
+```
+
+```{r}
+#| label: summary_statistic_cleaned_dataset
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+
+plot(model_file, "rhat")
+
+```
 # References

### 2024-11-26 scripts/03-clean_data.R

@@ -4,7 +4,7 @@
 # Date: November 26, 2024
 # Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
+# Pre-requisites: None
 
 #### Workspace setup ####
 library(tidyverse)
@@ -20,7 +20,8 @@ print(data)
 data$"rated_high" <- ifelse(data$rating > 4, 1, 0)
 
 # drop unnecessary columns 
-data <- data %>% select(-c(isbn, original_publish_year))
+data <- data %>% select(-c(author, isbn, original_publish_year))
 
 #### Save data in parquet file ####
 write_parquet(data, "data/analysis_data/analysis_data.parquet") 
+

### 2024-11-26 scripts/06-model_data.R

@@ -1,11 +1,10 @@
 #### Preamble ####
 # Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Author: Hyunje Park
+# Date: November 26, 2024
+# Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites:
 
 
 #### Workspace setup ####
@@ -13,17 +12,16 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 ### Model data ####
 first_model <-
   stan_glm(
-    formula = flying_time ~ length + width,
+    rated_high ~ cover + rating_count + publish_year + pages,
     data = analysis_data,
-    family = gaussian(),
+    family = binomial(link = 'logit'),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
     seed = 853
   )
 
@@ -31,7 +29,7 @@ first_model <-
 #### Save model ####
 saveRDS(
   first_model,
-  file = "models/first_model.rds"
+  file = "models/model.rds"
 )
 
 

### 2024-11-27 paper/paper.qmd
fixed introduction

@@
   - Hyunje Park
-thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating)."
+thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper examines the rating of childrens' books using the .
+By using logistic regression and data from the Alex Cookson (CITATION), I analyzed the relationship between various characteristics of a childrens' book, and whether or not it influenced if the book had a high rating or not.
+The insight from this research not only clarify what makes a high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature"
 format: pdf
@@
 data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
-print(data)
 ```
@@
 # Introduction
+
+## Estimand
+
+# Model
+
+# Results
+
+# Discussion
+
+# Appendix
 
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset
+#| label: summary_statistic_cleaned_dataset2
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset
+#| label: summary_statistic_cleaned_dataset3
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset
+#| label: summary_statistic_cleaned_dataset4
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset
+#| label: summary_statistic_cleaned_dataset5
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset
+#| label: summary_statistic_cleaned_dataset6
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset
+#| label: summary_statistic_cleaned_dataset7
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"

### 2024-11-27 paper/paper.qmd
finished introduction

@@
 
-## Estimand
+For generations, children's books have been a catalyst in children's development.
+Through captivating fairytales and fables of stories about adventures, heroes, magical forests and magic, children gain experiences on feelings and thoughts, learning to cope with inhibitions, vulnerability and shyness (CITATION).
+Beyond educational purposes, children's literature can positively influence mental wellbeing, feelings and behavior.
+Given these significant developmental benefits, it can be said that the quality of the children's book matters greatly; choosing a well-written book can affect how it nurtures the next generation of mature, emotionally resilient individuals.
+This is why book rating systems hold significant importance; allowing readers to rate books on a scale from 0-5 scale (most commonly used scale) helps parents and educators assess whether a book is worth giving to children.
+
+In this 0-5 rating system, a score of 4 or above is often seen as the benchmark for a "highly rated" book.
+This is influenced by central tendency bias, where people naturally gravitate towards a moderate score, avoiding extremes like 0 or 5 to appear more balanced and objective.
+A rating such as 4, in particular, suggests a strong endorsement without overstepping into exaggeration.
+Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being "highly rated"?
+
+In this paper, I analyzed how the characteristics of a book, such as book type, page count, publishing year, and rating counts affected the likelihood of a book being "highly-rated", using the Children's Book Ratings Data (CITATION).
+First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in (SECTION 2).
+Then, a logistic regression model was created to predict the probability of the book being "highly-rated", based on the chosen book characteristic variables.
+
+The logistic regression model showed that ___ The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.
+
+This research paper is structured as follows: (SECTION 2) contains an overview of the dataset and some tables and graphs used to illustrate the variables employed in this analysis.
+(SECTION 3) describes and justifies the logistic regression model that was produced in this report.
+(SECTION 4) highlights the result of the model, (SECTION 5) discusses some of the outcomes, weaknesses, and (SECTION APPENDIX) contains additional information on model details.
+
+# Estimand
 

### 2024-11-27 paper/paper.qmd
fixed sample size in model_data.R

@@
 
+The estimand of this paper is the probability that a book is highly-rated (has an average rating of over 4 on a 0-5 scale), based on book characteristics.
+It is difficult to measure the exact number as there are millions of children's books that are published and not all of them will be accessed due to various issues.
+For examples, children's books from different countries may have different ratings.
+Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset (CITATION)
+
+# Data
+
+Data analysis is performed using statistical programming language , along with packages
+
 # Model
@@
 data %>% head(5)
+
+data
 ```

### 2024-11-27 scripts/06-model_data.R

@@ -14,6 +14,10 @@ library(rstanarm)
 #### Read data ####
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
+analysis_reduced <- analysis_data |> 
+  slice_sample(n= 2500)
+  
+  
 ### Model data ####
 first_model <-
   stan_glm(

### 2024-11-27 paper/paper.qmd
fixed launch issue with paper.qmd

@@
 A rating such as 4, in particular, suggests a strong endorsement without overstepping into exaggeration.
-Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being "highly rated"?
+Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being "highly-rated" (a score above 4)?
 
-In this paper, I analyzed how the characteristics of a book, such as book type, page count, publishing year, and rating counts affected the likelihood of a book being "highly-rated", using the Children's Book Ratings Data (CITATION).
+In this paper, I analyzed how the characteristics of a book, such as book type, page count, publishing year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data (CITATION).
 First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in (SECTION 2).
@@
 
-The logistic regression model showed that ___ The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.
+The logistic regression model showed that ___ .The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.
 
@@
 #| fig-cap: "Preview of the Cleaned Dataset"
+#| message: false
 #| echo: false
+#| warning: false
 
 # TABLE 1: CLEANED DATASET
-data %>% head(5)
+data %>% 
+  head(5) %>%
+  kable(booktabs = TRUE, linesep = "") %>%
+  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
 
-data
 ```
@@
 \newpage
-```{r}
-#| label: summary_statistic_cleaned_dataset3
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
-#| echo: false
-
-model_file <- readRDS(file = here::here("models/model.rds"))
-
-modelsummary(
-  list (
-    "Book is High-Rated" = model_file
-  ),
-  statistic = "mad"
-)
-
-```
 
@@
 #| echo: false
+
+# delete this later
+model_file <- readRDS(file = here::here("models/model.rds"))
 
@@
 #| echo: false
+
+analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
 
@@
 ```
+
+-->
 # References

### 2024-11-27 scripts/03-clean_data.R

@@ -20,7 +20,7 @@ print(data)
 data$"rated_high" <- ifelse(data$rating > 4, 1, 0)
 
 # drop unnecessary columns 
-data <- data %>% select(-c(author, isbn, original_publish_year))
+data <- data %>% select(-c(title, author, isbn, original_publish_year))
 
 #### Save data in parquet file ####
 write_parquet(data, "data/analysis_data/analysis_data.parquet") 

### 2024-11-27 paper/paper.qmd
fixed tables in paper.qmd

@@
 # TABLE 1: CLEANED DATASET
-data %>% 
+first_half <- data %>% select(1:6)
+
+first_half %>% 
   head(5) %>%
   kable(booktabs = TRUE, linesep = "") %>%
-  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
+  kable_styling(bootstrap_options = "condensed", full_width = FALSE)
+```
 
+```{r}
+#| message: false
+#| echo: false
+#| warning: false
+
+# CONTINUTATION OF TABLE 1: CLEANED DATASET
+second_half <- data %>% select(7:12)
+
+second_half %>% 
+  head(5) %>%
+  kable(booktabs = TRUE, linesep = "") %>%
+  kable_styling(bootstrap_options = "condensed", full_width = FALSE)
 ```
@@
 
-data %>% 
-  select(-c(title)) %>% 
-  summary(rated-high) %>% 
+summary_table <- data %>%
+  filter(!is.na(rated_high)) %>%  
+  group_by(rated_high) %>%       
+  summarise(
+    avg_pages = mean(pages, na.rm = TRUE),          
+    avg_publish_year = mean(publish_year, na.rm = TRUE),
+    avg_rating_count = mean(rating_count, na.rm = TRUE)  
+  )
+
+summary_table %>% 
   kable(booktabs = TRUE, linesep = "") %>% 

### 2024-11-27 scripts/03-clean_data.R

@@ -20,7 +20,7 @@ print(data)
 data$"rated_high" <- ifelse(data$rating > 4, 1, 0)
 
 # drop unnecessary columns 
-data <- data %>% select(-c(title, author, isbn, original_publish_year))
+data <- data %>% select(-c(title, publisher, author, isbn, original_publish_year))
 
 #### Save data in parquet file ####
 write_parquet(data, "data/analysis_data/analysis_data.parquet") 

### 2024-11-27 paper/paper.qmd
fixed a rating graph in paper.qmd

@@
   kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
-
 ```
@@
 # Data {#sec-data}
+
+```{r}
+#| label: summary_statistic_cleaned_dataset125
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+
+data2 <- data %>% filter(rating >= 4)
+data3 <- data %>% filter(rating < 4)
+data2 <- data2 %>% mutate(group = "High Rating (>= 4)")
+data3 <- data3 %>% mutate(group = "Low Rating (< 4)")
+
+# Combine the two datasets
+combined_data <- bind_rows(data2, data3)
+
+avg_publish_years <- combined_data %>%
+  group_by(group) %>%
+  summarise(avg_publish_year = mean(publish_year, na.rm = TRUE))
+
+# Create a combined scatter plot with facets
+ggplot(combined_data, aes(x = publish_year, y = rating)) +
+  geom_point() +
+  theme_minimal() +
+  facet_wrap(~group, ncol = 1, scales = "free_y") +
+  geom_vline(data = avg_publish_years, aes(xintercept = avg_publish_year), 
+             color = "red", linetype = "dashed", size = 1)
+
+```
 
@@
 
-data2 <- data %>% filter(rating > 4 )
+data2 <- data %>% filter(rating >= 4)
 
@@
 ggplot(data2, aes(x = rating, y = rating_count)) +
-  geom_point() +
-  geom_smooth( se =FALSE, color = "red", size = 1)
+  geom_point()
 
 ggplot(data2, aes(x = rating, y = pages)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE, color = 'red', size = 1)
+  geom_point()
 
@@
   theme_minimal()
-
-cover_counts <- data %>%
-  group_by(rated_high, cover) %>%
-  summarise(count = n()) %>%
-  ungroup()
-
-ggplot(cover_counts, aes(x = cover, y = count, fill = cover)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  facet_wrap(~ rated_high) +
-  labs(title = "Count of Hardcover and Paperback by Rated High",
-       x = "Cover Type",
-       y = "Count") +
-  theme_minimal()
-
 ```

### 2024-11-27 paper/paper.qmd
finished data section rough draft

@@
 
-# Estimand
+## Estimand
 
@@
 
-# Data
+# Data {#sec-data}
 
-Data analysis is performed using statistical programming language , along with packages
+The dataset used in this paper was obtained from COOKSON (CITATION), who sourced it from Goodreads (CITATION).
+Cookson's dataset contained over 9,000+ records of children's books that contained information on the book such as title, author, ratings, publisher and more.
+In the initial step, data-cleaning was performed and relevant variables were selected.
+First, entries with missing information were filtered out, and variables that were irrelevant to this study was also removed, which included variables such as book title.
+After cleaning, there were 9240 entries in the cleaned dataset.
 
-# Model
+Data analysis is performed using statistical programming language , along with packages ___
 
-# Results
-
-# Discussion
-
-# Appendix
+## Data Cleaning
 
@@
 #| label: cleaned_dataset-preview
-#| fig-cap: "Preview of the Cleaned Dataset"
+#| tbl-cap: "Preview of the Cleaned Children's Book Dataset"
 #| message: false
@@
 
+data
 # TABLE 1: CLEANED DATASET
@@
 # CONTINUTATION OF TABLE 1: CLEANED DATASET
+# cant fit it in one line, put it next
 second_half <- data %>% select(7:12)
@@
 ```
+
+Table 1 (CROSS REFERENCE) presents the first 5 rows from the cleaned dataset, that contains information on Children's book.
+
+## Variable
+
+This analysis focuses on the following variables, with a focus on `rated_high` as the dependent variable
+
+- `rated_high`: A binary variable telling us if a book is rated high or not (above a 4 rating)
+  - `0`: The book has a rating below 4
+  - `1`: The book has a rating greater or equal to 4
+
+- `pages`: An integer that represents the number of pages for the book
+
+- `rating_count`: An integer that represents how many ratings the book received
+
+- `publish_year`: An integer that represents the year the book was published
+
+- `cover`: A categorical variable that represents the type of the book, which can include:
+  - `Ebook`: The book is in a digital format.
+  - `Kindle`: The book is only available through Kindle e-reader tablet.
+  - `Board book`: The book is a picture book designed for the youngest of children, babies, infants.
+  - `Hardcover`: The book has a rigid protective cover.
+  - `Paperback`: The book is has a thick paper cover.
 
@@
     avg_publish_year = mean(publish_year, na.rm = TRUE),
-    avg_rating_count = mean(rating_count, na.rm = TRUE)  
+    avg_rating_count = mean(rating_count, na.rm = TRUE),
+    avg_cover = names(sort(table(cover), decreasing = TRUE)[1])
   )
@@
   kable(booktabs = TRUE, linesep = "") %>% 
-  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
+  kable_styling(bootstrap_options = "condensed", full_width = FALSE)
 ```
 
-# Data {#sec-data}
+Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset.
+It showed that books that were considered "high rated" had more pages on average than low rated books.
+Furthermore, high rated books were on average published 2 years before low rated books, around the year 2003.
+In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x.
+The most common type of book cover also turned out to be hard covers.
+These variables are key in the analysis, and are further shown in (CITE HERE)
+
+## Data Analysis
 
 ```{r}
-#| label: summary_statistic_cleaned_dataset125
+#| label: fig-most-common-covers
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+
+data2 <- data %>% filter(rating >= 4)
+
+ggplot(data2, aes(y = cover)) + 
+  geom_bar() +
+  theme_minimal()
+
+```
+
+(CITATION HERE PICTURE ABOVE) shows the number of cover types for "high-rated" books (rated_high = 1).
+It is evident that Paperback and Hardcover books make up the majority of "high-rated" books, which could potentially reflect the aesthetic and collectible value of Paperback/Hardcover books over something non-physical like an Ebook.
+This illustrates that physical books could be more appealing for readers due to ownership bias, greatly increasing their rating.
+This finding also reflects the result from (TABLE)
+
+```{r}
+#| label: fig-page-count
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+avg_pages <- aggregate(pages ~ rated_high, data = data, FUN = mean, na.rm = TRUE)
+
+ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
+  geom_bar(stat = "identity") +
+  labs(
+    title = "Average Pages by High Rated",
+    x = "High Rated (1 = Yes, 0 = No)",
+    y = "Average Pages",
+    fill = "High Rated"
+  ) +
+  theme_minimal()
+
+```
+
+(CTATION HERE) shows that generally, "high-rated" books have more page count than low-rated books.
+This suggests that higher page counts could correlate with higher ratings as more pages could allow deeper storytelling, richer world-building or character development, which can result in a more immersive experience for the reader.
+This graph illustrates the importance for authors to use more pages for properly structured narratives.
+
+```{r}
+#| label: fig-publish-year
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
              color = "red", linetype = "dashed", size = 1) 
+```
+(CITATION) shows the relationship between year of publish and the book's rating.
+Where the horizontal axis shows the year of publishment, and vertical axis shows the rating of the book.
+By looking at the red line of fit (average year of publishment), "high-rated" books tend to be published before low-rated books.
+This could be due to selective survival where older books that remain in circulation could be considered "classics" and have stood the test of time.This is further discussed in (DISCUSSION HERE)
 
+```{r}
+#| label: fig-rating-count
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+#| 
+data2 <- data %>% filter(rating >= 4)
+
+ggplot(data, aes(x = rating, y = rating_count)) +
+  geom_point() 
 ```
+
+(FIGURE 5) shows the relationship between the rating of a book and the number of ratings it received.
+The red line indicates the cut-off for a book to be considered "highly-rated".
+It is apparent that books that are considered "highly_rated" (right of the red line) have far more ratings on average than low-rated books.
+
+# Model {#sec-model}
+
+# Results {#sec-result}
+
+# Discussion {#sec-discussion}
+
+# Appendix {#sec-appendix}
 
@@
 
-ggplot(data2, aes(x = publish_year, y = rating)) +
-  geom_point() +
-  theme_minimal()
-
 ggplot(data2, aes(x = rating, y = rating_count)) +
@@
 
-ggplot(data2, aes(y = cover)) + 
-  geom_bar() +
-  theme_minimal()
-
-avg_pages <- aggregate(pages ~ rated_high, data = data, FUN = mean, na.rm = TRUE)
-
-ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
-  geom_bar(stat = "identity") +
-  labs(
-    title = "Average Pages by High Rated",
-    x = "High Rated (1 = Yes, 0 = No)",
-    y = "Average Pages",
-    fill = "High Rated"
-  ) +
-  theme_minimal()
 ```

### 2024-11-28 paper/paper.qmd
fixed alignment issue with model

@@
 abstract: "This paper examines the rating of childrens' books using the .
-By using logistic regression and data from the Alex Cookson (CITATION), I analyzed the relationship between various characteristics of a childrens' book, and whether or not it influenced if the book had a high rating or not.
-The insight from this research not only clarify what makes a high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature"
+By using a Bayesian logistic regression and data from the Alex Cookson (CITATION), I analyzed the relationship between various characteristics of a childrens' book, and whether or not it influenced if the book had a high rating or not.
+The insight from this research not only clarify what makes a high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature."
 format: pdf
@@
 library(modelsummary)
+
+library(tidyverse)
+library(here)
+library(rstanarm)
+library(modelsummary)
+library(ggplot2)
+library(knitr)
 
@@
 
+Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset.
+It showed that books that were considered "high rated" had more pages on average than low rated books.
+Furthermore, high rated books were on average published 2 years before low rated books, around the year 2003.
+In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x.
+The most common type of book cover also turned out to be hard covers.
+These variables are key in the analysis, and are further shown in (CITE HERE)
+
 ```{r}
@@
 
-Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset.
-It showed that books that were considered "high rated" had more pages on average than low rated books.
-Furthermore, high rated books were on average published 2 years before low rated books, around the year 2003.
-In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x.
-The most common type of book cover also turned out to be hard covers.
-These variables are key in the analysis, and are further shown in (CITE HERE)
+\newpage
 
@@
 
+\newpage
+
 # Model {#sec-model}
 
+This study employed a Bayesian logistic regression model to analyze the relationship between Children's book's "highly-rated" status and the characteristic of the book. The model is as follows:
+
+\begin{align} 
+y_i|\pi_i &\sim \mbox{Bern}(\pi_i) \label{eq1} \\
+\mbox{logit}(\pi_i) &= \beta_0 + \beta_1 \times \mbox{pages$_i$} \\
+&\quad + \beta_2 \times \mbox{rating\_count$_i$} + \beta_3 \times \mbox{publish\_year$_i$} \\
+&\quad + \beta_4 \times \mbox{coverEbook$_i$} + \beta_5 \times \mbox{coverKindleEdition$_i$} \\
+&\quad + \beta_6 \times \mbox{coverBoardBook$_i$} + \beta_7 \times \mbox{coverHardcover$_i$} \\
+&\quad + \beta_8 \times \mbox{coverPaperback$_i$} \label{eq2} \\
+\beta_0 &\sim \mbox{Normal}(0, 2.5) \label{eq3} \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \label{eq4} \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \label{eq5}\\
+\beta_3 &\sim \mbox{Normal}(0, 2.5) \label{eq6}\\
+\beta_4 &\sim \mbox{Normal}(0, 2.5) \label{eq7}\\
+\beta_5 &\sim \mbox{Normal}(0, 2.5) \label{eq8}\\
+\beta_6 &\sim \mbox{Normal}(0, 2.5) \label{eq9}\\
+\beta_7 &\sim \mbox{Normal}(0, 2.5) \label{eq10}\\
+\beta_8 &\sim \mbox{Normal}(0, 2.5) \label{eq11}
+\end{align}
+
+## Prior Distribution
+
+The rstanarm package (CITATION) was used in order to run the regression model mentioned above.
+The default priors of the rstanarm package was used (CITATION).
+These default priors are designed to be weakly informative, meaning they provide enough information to regularize the model and prevent extreme estimates, while being flexible to let the data drive the inference.
+By default, priors for regression coefficients are centered around 0 with a standard deviation of 2.5, which is shown in equations (Equation LIST).
+
+## Model Justification
+
+The predictor variables shown in (LIST HERE) were chosen due to the number of studies regarding their influence on ratings of books.
+
+More specifically, I expect that
+
 # Results {#sec-result}
+
+After running the regression model above, we receive the coefficient values showcased in Table X.
 
@@
 
+model_file <- readRDS(file = here::here("models/model.rds"))
+
 plot(model_file, "trace", "(Intercept)")

### 2024-11-28 scripts/06-model_data.R
finished result

@@ -15,7 +15,7 @@ library(rstanarm)
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
 
 analysis_reduced <- analysis_data |> 
-  slice_sample(n= 2500)
+  slice_sample(n = 7000)
   
   
 ### Model data ####
@@ -26,7 +26,7 @@ first_model <-
     family = binomial(link = 'logit'),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
     prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 853
+    seed = 529
   )
 
 

### 2024-11-28 paper/paper.qmd
finished discussion

@@
 library(modelsummary)
+library(dplyr)
 
@@
 In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x.
-The most common type of book cover also turned out to be hard covers.
+Kindle covers had the highest proportion of "high-rated" books out of any other cover types.
 These variables are key in the analysis, and are further shown in (CITE HERE)
@@
     avg_rating_count = mean(rating_count, na.rm = TRUE),
-    avg_cover = names(sort(table(cover), decreasing = TRUE)[1])
+    highest_proportion_cover = data %>%
+      group_by(cover) %>%
+      summarise(high_rated_pct = mean(rated_high, na.rm = TRUE)) %>%
+      slice_max(high_rated_pct, n = 1) %>%
+      pull(cover)
   )
@@
 
-data2 <- data %>% filter(rating >= 4)
+data2 <- data %>%filter(rating >= 4)
 
-ggplot(data2, aes(y = cover)) + 
-  geom_bar() +
-  theme_minimal()
+cover_proportions <- data %>%
+  group_by(cover) %>%
+  summarise(high_rated_pct = mean(rated_high, na.rm = TRUE)) %>%
+  arrange(desc(high_rated_pct))  # Sort by highest proportion
+
+# Create the horizontal bar plot
+ggplot(cover_proportions, aes(x = high_rated_pct, y = reorder(cover, high_rated_pct), fill = high_rated_pct)) +
+  geom_bar(stat = "identity", show.legend = FALSE) +
+  labs(
+    title = "Proportion of High-Rated Books by Cover Type",
+    x = "Proportion of High-Rated Books",
+    y = "Cover Type"
+  ) +
+  scale_x_continuous(labels = scales::percent_format()) +  # Format x-axis as percentages
+  theme_minimal() +
+  theme(
+    axis.text = element_text(size = 10),
+    plot.title = element_text(hjust = 0.5, size = 14)
+  )
 
@@
 
-After running the regression model above, we receive the coefficient values showcased in Table X.
+After running the regression based on the model shown above, we get the coefficient values showcased in Table X (CITE HERE).
+
+COEFFICIENT RANGE (CITE) represent the 90% probability intervals of the estimates, where a coefficient is considered statistically significant if the range excludes 0.
+In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being "highly-rated" when positive and "low-rated" when negative.
+
+With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being "highly-rated", assuming all else held constant, reflecting the analysis that was seen in DATA (CITE HERE).
+In contrast, the number of pages of a book, and the number of ratings no statistically significant influence on a book being "highly-rated".
+
+Although the publish year was not statistically significant according to the GRAPH (CITE), it exhibited a slight negative relationship (coefficient: -0.01), consistent with previous findings (CITE) that "high-rated" books tend to have earlier publication years compared to "low-rated" ones.
+
+```{r}
+#| label: summary_statistic_cleaned_dataset3
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+
+model_file <- readRDS(file = here::here("models/model.rds"))
+
+modelsummary(
+  list (
+    "Book is High-Rated" = model_file
+  ),
+  statistic = "mad"
+)
+```
 
@@
 
+## Rating Count and Page Count
+
+As shown by SECTIOM  (RESULTS), the number of ratings a book receives and its page length had no statistical significance on a book being highly-rated.
+In particular, these factors are likely independent of how readers perceive its quality or enjoyment.
+Short books can be impactful and concise, whereas longer books can offer richer detail.
+
+Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions.
+Therefore, once a book has many reviews, its average rating stabilizes, making the number of ratings irrelevant to the overall evaluation.
+
+## Type of Cover
+
+The results in SECTION (RESULTS), indicated a big positive relationship between book cover types and its "highly-rated" status.
+In particular, the "Kindle Edition" book cover had the highest coefficient (NUMBER HERE).
+A potential explanation could be that ebooks (such as Kindle Edition) are often preferred over physical books for their convenience, affordability and accessibility.
+Additionally ebooks are often cheaper due to saving material costs and saving physical space.
+In Middle-Eastern countries, 74.6% students preferred e-books in terms of easy to carry and 80.6% of them spent more time reading from e-books than printed books (CITATION HERE).
+Thus, it could appear that e-books have an advantage in attracting those seeking convenience and personalization in their reading, potentially explaining its high-rating over any other book cover types.
+
+## Publish Year
+
+While the result in SECTION (RESULT) showed that the publish year was statistically insignificant, (GRAPH) a small negative correlation which was expected.
+In particular, high-rated books had an older publish year than lowly-rated books.
+
+The first explanation could be that older books have had more time to be appreciated, analyzed and critiqued, which could allow their work to be better established than current generation books.
+Many older books that receive high ratings have stood the test of time, becoming classics that made its name for generations.
+
+The second explanation could be that older books may benefit from nostalgia, where readers could assign higher ratings due to a stronger emotional connection and cultural significance they hold.
+While this
+
 # Appendix {#sec-appendix}
 
-```{r}
-#| label: summary_statistic_cleaned_dataset2
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
-#| echo: false
+\newpage
 
-data2 <- data %>% filter(rating >= 4)
+## Posterior Predictive Check
 
-ggplot(data2, aes(x = rating, y = rating_count)) +
-  geom_point()
-
-ggplot(data2, aes(x = rating, y = pages)) +
-  geom_point()
-
-```
-
-\newpage
+We used a posterior predictive check in FIGURE (CITE) to evaluate how well the model fits the data.
+This compares the observed data Y (CHANGE) against the replicated data y-REP (CHANGE) which was generated by our model in SECTION 3 (CITE).
+The poterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.
 
@@
 
--->
+```{r}
+#| label: summary_statistic_cleaned_dataset7
+#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| echo: false
+
+modelplot(model_file, conf_level = 0.9, coef_omit = c(5,8)) +
+  labs(x= "90% percent credibility interval")
+```
+
 # References

### 2024-11-28 paper/paper.qmd
finished rough draft

@@
 
+## Comparison of the Posterior vs Prior
+
+In FIGURE BELOW (CITE) we compared the posterior with the prior, to examine how the estimates change once data is taken into account (CITE ALEXANDER).
+Most of the variables do not vary even after data was taken into account, showing that the observed data matches the expectations of a "highly-rated" book.
+
 ```{r}
@@
 
+## Markov Chain Monte Carlo Convergence Check
+
+FIGURE X AND Y are the trace plot of the model and Rhat plot of the model respectively.
+
+The trace plot shows osciliating horizontal lines, with overlaps between chains, showing no signs of issues with the model.
+
+Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 (CITE ALENXANDER)
+
 ```{r}

### 2024-11-29 paper/paper.qmd
generated new pdf
fixed typos

@@
 date-format: long
-abstract: "This paper examines the rating of childrens' books using the .
-By using a Bayesian logistic regression and data from the Alex Cookson (CITATION), I analyzed the relationship between various characteristics of a childrens' book, and whether or not it influenced if the book had a high rating or not.
-The insight from this research not only clarify what makes a high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature."
+abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (CITATION).
+By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating.
+The results showed that the book's cover type had the biggest positive impact on a book's rating.
+The insight from this research not only clarify the key elements that make high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature and writing choices."
 format: pdf
@@
 library(dplyr)
-
-library(tidyverse)
 library(here)
@@
 library(knitr)
+library(scales)
 
@@
 Through captivating fairytales and fables of stories about adventures, heroes, magical forests and magic, children gain experiences on feelings and thoughts, learning to cope with inhibitions, vulnerability and shyness (CITATION).
-Beyond educational purposes, children's literature can positively influence mental wellbeing, feelings and behavior.
 Given these significant developmental benefits, it can be said that the quality of the children's book matters greatly; choosing a well-written book can affect how it nurtures the next generation of mature, emotionally resilient individuals.
-This is why book rating systems hold significant importance; allowing readers to rate books on a scale from 0-5 scale (most commonly used scale) helps parents and educators assess whether a book is worth giving to children.
+This is why book rating systems hold significant importance; allowing readers to rate books on a scale from 0-5 (most commonly used scale) helps parents and educators assess whether a book is worth giving to children.
 
@@
 A rating such as 4, in particular, suggests a strong endorsement without overstepping into exaggeration.
-Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being "highly-rated" (a score above 4)?
+Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being categorized as "highly-rated" (a score above 4)?
 
-In this paper, I analyzed how the characteristics of a book, such as book type, page count, publishing year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data (CITATION).
+In this paper, I analyzed how the characteristics of a book, such as cover type, page count, publish year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data (CITATION).
 First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in (SECTION 2).
@@
 
-The estimand of this paper is the probability that a book is highly-rated (has an average rating of over 4 on a 0-5 scale), based on book characteristics.
-It is difficult to measure the exact number as there are millions of children's books that are published and not all of them will be accessed due to various issues.
-For examples, children's books from different countries may have different ratings.
-Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset (CITATION)
+The estimand of this paper is the probability that a children's book is "highly-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics.
+It is difficult to measure the exact number as there are millions of children's books that are published and not all of them will be accessed.
+For examples, children's books may have variations in ratings across countries.
+Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset (CITATION).
 
@@
 The dataset used in this paper was obtained from COOKSON (CITATION), who sourced it from Goodreads (CITATION).
-Cookson's dataset contained over 9,000+ records of children's books that contained information on the book such as title, author, ratings, publisher and more.
+Cookson's dataset contained over 9,000 records of children's books that contained information of books such as title, author, ratings, publisher and more.
 In the initial step, data-cleaning was performed and relevant variables were selected.
-First, entries with missing information were filtered out, and variables that were irrelevant to this study was also removed, which included variables such as book title.
-After cleaning, there were 9240 entries in the cleaned dataset.
+First, entries with missing information were filtered out, and variables that were irrelevant to this study were also removed, which included variables such as book title.
+Then, a new variable called "highly-rated" was created, which was a binary variable indicating if the book had a rating over 4 (1 if it exceeded 4, 0 else).
+After cleaning and creating this new variable, there were 9240 entries in the cleaned dataset.
 
@@
 
-data
 # TABLE 1: CLEANED DATASET
@@
 
-Table 1 (CROSS REFERENCE) presents the first 5 rows from the cleaned dataset, that contains information on Children's book.
+Table 1 (CROSS REFERENCE) presents the first 5 rows from the cleaned dataset, which contains information on Children's book.
 
@@
 
-- `rating_count`: An integer that represents how many ratings the book received
+- `rating_count`: An integer representing the number of ratings the book received
 
-- `publish_year`: An integer that represents the year the book was published
+- `publish_year`: An integer representing the year the book was published
 
-- `cover`: A categorical variable that represents the type of the book, which can include:
+- `cover`: A categorical variable representing the type of the book, which can include:
   - `Ebook`: The book is in a digital format.
@@
 Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset.
-It showed that books that were considered "high rated" had more pages on average than low rated books.
-Furthermore, high rated books were on average published 2 years before low rated books, around the year 2003.
-In addition to this, the amount of ratings high-rated books received far exceed low rated books, at about 4x.
-Kindle covers had the highest proportion of "high-rated" books out of any other cover types.
-These variables are key in the analysis, and are further shown in (CITE HERE)
+It showed that books that were considered "high rated" had more pages on average than low-rated books.
+Furthermore, high rated books were on average published 2 years before low rated books, with publish year of 2005 and 2003 for the low-rated books and high-rated books respectively.
+High-rated books also received far more ratings on average at 8000 ratings, more than four times of low-rated books at an average of 2000 reviews per book.
+Lastly, Kindle covers had the highest proportion of "high-rated" books out of any other cover types (as well as low-rated books).
+These variables are key in the analysis, and are further mentioned in (CITE HERE)
 
 ```{r}
-#| label: summary_statistic_cleaned_dataset
+#| label: summary_statistic_dataset
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
 #| echo: false
-
+#| warning: false
 summary_table <- data %>%
@@
 #| echo: false
+#| warning: false
 
-data2 <- data %>%filter(rating >= 4)
+data3 <- data %>%
+  filter(!is.na(cover) & !is.na(rated_high))
 
-cover_proportions <- data %>%
+cover_proportions <- data3 %>%
   group_by(cover) %>%
-  summarise(high_rated_pct = mean(rated_high, na.rm = TRUE)) %>%
-  arrange(desc(high_rated_pct))  # Sort by highest proportion
+  summarise(
+    total_books = n(),                                # Total number of books for each cover type
+    high_rated_books = sum(rated_high, na.rm = TRUE), # Total number of highly-rated books for each cover type
+    high_rated_pct = high_rated_books / total_books   # Proportion of highly-rated books
+  ) %>%
+  arrange(desc(high_rated_pct))  # Sort by the highest proportion
 
-# Create the horizontal bar plot
+# Create the bar plot
 ggplot(cover_proportions, aes(x = high_rated_pct, y = reorder(cover, high_rated_pct), fill = high_rated_pct)) +
   geom_bar(stat = "identity", show.legend = FALSE) +
+  geom_text(aes(label = percent(high_rated_pct, accuracy = 0.1)), 
+            hjust = -0.1, 
+            size = 3.5) +  # Add percentage labels
   labs(
-    title = "Proportion of High-Rated Books by Cover Type",
-    x = "Proportion of High-Rated Books",
+    title = "Proportion of Highly-Rated Books by Cover Type",
+    x = "Proportion of Highly-Rated Books",
     y = "Cover Type"
   ) +
-  scale_x_continuous(labels = scales::percent_format()) +  # Format x-axis as percentages
+  scale_x_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) + # Format x-axis as percentages
   theme_minimal() +
@@
     axis.text = element_text(size = 10),
-    plot.title = element_text(hjust = 0.5, size = 14)
+    plot.title = element_text(hjust = 0.5, size = 14),
+    plot.margin = margin(10, 50, 10, 10)
   )
@@
 
-(CITATION HERE PICTURE ABOVE) shows the number of cover types for "high-rated" books (rated_high = 1).
-It is evident that Paperback and Hardcover books make up the majority of "high-rated" books, which could potentially reflect the aesthetic and collectible value of Paperback/Hardcover books over something non-physical like an Ebook.
-This illustrates that physical books could be more appealing for readers due to ownership bias, greatly increasing their rating.
+(CITATION HERE PICTURE ABOVE) shows the proportion of "highly-rated" books for each cover type.
+`Kindle Edition` books had the highest proportions of highly-rated books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively.
+This illustrates that generally, digitally formatted books had higher proportions of "highly-rated" books compared to physical formats.
 This finding also reflects the result from (TABLE)
@@
 #| echo: false
+#| warning: false
+
 avg_pages <- aggregate(pages ~ rated_high, data = data, FUN = mean, na.rm = TRUE)
 
+# Create the bar plot with text labels
 ggplot(avg_pages, aes(x = factor(rated_high), y = pages, fill = factor(rated_high))) +
   geom_bar(stat = "identity") +
+  geom_text(aes(label = round(pages, 1)), vjust = -0.5, size = 4) +  # Add labels above the bars
   labs(
@@
   theme_minimal()
-
 ```
 
-(CTATION HERE) shows that generally, "high-rated" books have more page count than low-rated books.
-This suggests that higher page counts could correlate with higher ratings as more pages could allow deeper storytelling, richer world-building or character development, which can result in a more immersive experience for the reader.
-This graph illustrates the importance for authors to use more pages for properly structured narratives.
+(CTATION HERE) shows that "high-rated" books have more page count than low-rated books.
+Highly-rated books had an average page count of 66.1, compared to the 57.6 average page count of low-rated books.
 
@@
 #| echo: false
+#| warning: false
 
@@
 data3 <- data %>% filter(rating < 4)
-data2 <- data2 %>% mutate(group = "High Rating (>= 4)")
-data3 <- data3 %>% mutate(group = "Low Rating (< 4)")
+data2 <- data2 %>% mutate(group = "High Rated Books (>= 4)")
+data3 <- data3 %>% mutate(group = "Low Rated Books (> 4)")
 
@@
 ```
-(CITATION) shows the relationship between year of publish and the book's rating.
-Where the horizontal axis shows the year of publishment, and vertical axis shows the rating of the book.
-By looking at the red line of fit (average year of publishment), "high-rated" books tend to be published before low-rated books.
-This could be due to selective survival where older books that remain in circulation could be considered "classics" and have stood the test of time.This is further discussed in (DISCUSSION HERE)
+(CITATION) shows the relationship between a book's rating and the publish year.
+The horizontal axis shows the publish year, and vertical axis shows the rating of the book.
+The graph is split into two vertically, the top plot showing ratings of "high-rated" books and low-rated books.
+Low-rated books showed a higher concentration of publish year towards the right, suggesting a higher average publish year.
+By looking at the red line of fit (average publish year), "high-rated" books tend to be published before low-rated books.
 
@@
 #| echo: false
-#| 
+#| warning: false
+
 data2 <- data %>% filter(rating >= 4)
@@
 ggplot(data, aes(x = rating, y = rating_count)) +
-  geom_point() 
+  geom_vline(xintercept = 4, color = "red", linetype = "dashed", size = 1) +
+  geom_point() +
+  theme_minimal()
 ```
@@
 
-Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions.
+Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions (CITATION).
 Therefore, once a book has many reviews, its average rating stabilizes, making the number of ratings irrelevant to the overall evaluation.
@@
 In Middle-Eastern countries, 74.6% students preferred e-books in terms of easy to carry and 80.6% of them spent more time reading from e-books than printed books (CITATION HERE).
-Thus, it could appear that e-books have an advantage in attracting those seeking convenience and personalization in their reading, potentially explaining its high-rating over any other book cover types.
+Thus, it could appear that e-books have an advantage in attracting those seeking convenience and personalization in their reading, potentially explaining its big relationship compared to any other book cover types.
 
@@
 The second explanation could be that older books may benefit from nostalgia, where readers could assign higher ratings due to a stronger emotional connection and cultural significance they hold.
-While this
+
+## Weaknesses and Next Steps
+
+Regional differences were not considered in this paper.
+A book that appeals a reader in a country might not have the same appeal in another due to the differences in cultural context, historical experiences or social norms.
+Furthermore, regional differences in terms of accessibility of books (such as quality of translated versions or availability) could also impact ratings.
+
+In terms of the dataset, the number of entries were relatively low (a little over 9,000 entries).
+This limited number of entries could have affected the accuracy of the results, where certain factors such as book cover types might have been significantly overrepresented or underrepresented, skewing the analysis.
+
+Future research should aim to collect more representative data, potentially including datasets from diverse sources.
+Additionally, regional factors related to the book should be investigated.
+By exploring these regional influences, we can get an broader insight as to how cultural context, historical experience and social norms play a role in book ratings.
+This can help make improvements for a broader international appeal.
 
 # Appendix {#sec-appendix}
-
-\newpage
 
@@
 This compares the observed data Y (CHANGE) against the replicated data y-REP (CHANGE) which was generated by our model in SECTION 3 (CITE).
-The poterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.
+The posterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.
 
@@
 
-# delete this later
 model_file <- readRDS(file = here::here("models/model.rds"))
@@
   theme(legend.position = "bottom")
-
 ```
@@
 
-The trace plot shows osciliating horizontal lines, with overlaps between chains, showing no signs of issues with the model.
+The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model.
 
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset7
+#| label: summary_statistic_cleaned_dataset72
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"

### 2024-11-29 paper/paper.qmd
fixed citations

@@
 The results showed that the book's cover type had the biggest positive impact on a book's rating.
-The insight from this research not only clarify the key elements that make high rated childrens' book so high rated, but also enhance future authors to push the boundaries of their literature and writing choices."
+The insight from this research not only clarify the key elements that make high rated childrens' book so high-rated, but also enhance future authors to push the boundaries of their literature and writing choices."
 format: pdf
+toc: true
 number-sections: true
@@
 library(here)
-library(rstanarm)
-library(modelsummary)
 library(ggplot2)
@@
 For generations, children's books have been a catalyst in children's development.
-Through captivating fairytales and fables of stories about adventures, heroes, magical forests and magic, children gain experiences on feelings and thoughts, learning to cope with inhibitions, vulnerability and shyness (CITATION).
+Through captivating fairytales and fables of stories about adventures, heroes, magical forests and magic, children gain experiences on feelings and thoughts, learning to cope with inhibitions, vulnerability and shyness [@citeliterature].
 Given these significant developmental benefits, it can be said that the quality of the children's book matters greatly; choosing a well-written book can affect how it nurtures the next generation of mature, emotionally resilient individuals.
@@
 
-In this paper, I analyzed how the characteristics of a book, such as cover type, page count, publish year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data (CITATION).
-First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in (SECTION 2).
-Then, a logistic regression model was created to predict the probability of the book being "highly-rated", based on the chosen book characteristic variables.
+In this paper, I analyzed how the characteristics of a book, such as cover type, page count, publish year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data [@citedata].
+First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in @sec-data.
+Then, a logistic regression model was created to predict the probability of the book being high-rated, based on the chosen book characteristic variables.
 
-The logistic regression model showed that ___ .The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.
+The logistic regression model showed that book covers had the biggest influence on the likelihood of the book being high-rated, notably, the `Kindle Edition` type.
+The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.
 
-This research paper is structured as follows: (SECTION 2) contains an overview of the dataset and some tables and graphs used to illustrate the variables employed in this analysis.
-(SECTION 3) describes and justifies the logistic regression model that was produced in this report.
-(SECTION 4) highlights the result of the model, (SECTION 5) discusses some of the outcomes, weaknesses, and (SECTION APPENDIX) contains additional information on model details.
+This research paper is structured as follows: @sec-data contains an overview of the dataset and some tables and graphs used to illustrate the variables employed in this analysis.
+@sec-model describes and justifies the logistic regression model that was produced in this report.
+@sec-result highlights the result of the model, @sec-discussion discusses some of the outcomes, weaknesses, and @sec-appendix contains additional information on model details.
 
@@
 For examples, children's books may have variations in ratings across countries.
-Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset (CITATION).
+Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset [@sec-data].
 
@@
 
-The dataset used in this paper was obtained from COOKSON (CITATION), who sourced it from Goodreads (CITATION).
+The dataset used in this paper was obtained from Cookson [@citedata].
 Cookson's dataset contained over 9,000 records of children's books that contained information of books such as title, author, ratings, publisher and more.
@@
 
-Data analysis is performed using statistical programming language , along with packages ___
+Data analysis is performed using statistical programming language , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales].
 
@@
 ```{r}
-#| label: cleaned_dataset-preview
+#| label: tbl-cleaned-dataset-preview
 #| tbl-cap: "Preview of the Cleaned Children's Book Dataset"
@@
 
-Table 1 (CROSS REFERENCE) presents the first 5 rows from the cleaned dataset, which contains information on Children's book.
+@tbl-cleaned-dataset-preview presents the first 5 rows from the cleaned dataset, which contains information on children's book.
 
@@
 
-Table 2 (CITATION) shows a summary of detailed statistics about the cleaned dataset.
-It showed that books that were considered "high rated" had more pages on average than low-rated books.
-Furthermore, high rated books were on average published 2 years before low rated books, with publish year of 2005 and 2003 for the low-rated books and high-rated books respectively.
+@tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset.
+It showed that books that were considered high-rated had more pages on average than low-rated books.
+Furthermore, high-rated books were on average published 2 years before low rated books, with publish year of 2005 and 2003 for the low-rated books and high-rated books respectively.
 High-rated books also received far more ratings on average at 8000 ratings, more than four times of low-rated books at an average of 2000 reviews per book.
-Lastly, Kindle covers had the highest proportion of "high-rated" books out of any other cover types (as well as low-rated books).
-These variables are key in the analysis, and are further mentioned in (CITE HERE)
+Lastly, Kindle covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books).
+These variables are key in the analysis, and are further mentioned in @sec-data.
 
 ```{r}
-#| label: summary_statistic_dataset
+#| label: tbl-summary-statistic
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
 
-(CITATION HERE PICTURE ABOVE) shows the proportion of "highly-rated" books for each cover type.
-`Kindle Edition` books had the highest proportions of highly-rated books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively.
-This illustrates that generally, digitally formatted books had higher proportions of "highly-rated" books compared to physical formats.
-This finding also reflects the result from (TABLE)
+@fig-most-common-covers shows the proportion of `high-rated` books for each cover type.
+`Kindle Edition` books had the highest proportions of `high-rated` books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively.
+This illustrates that generally, digitally formatted books had higher proportions of `high-rated` books compared to physical formats.
+This finding also reflects the result from @tbl-summary-statistic.
 
@@
 
-(CTATION HERE) shows that "high-rated" books have more page count than low-rated books.
+@fig-page-count shows that `high-rated` books have more page count than low-rated books.
 Highly-rated books had an average page count of 66.1, compared to the 57.6 average page count of low-rated books.
@@
 
-data2 <- data %>% filter(rating >= 4)
-data3 <- data %>% filter(rating < 4)
-data2 <- data2 %>% mutate(group = "High Rated Books (>= 4)")
-data3 <- data3 %>% mutate(group = "Low Rated Books (> 4)")
+#removing NA values
+data_combined <- data %>%
+  filter(!is.na(rated_high), !is.na(publish_year), publish_year >= 1980) %>%
+  mutate(
+    rating_category = ifelse(rated_high == 1, "High-Rated", "Not High-Rated")
+  )
 
-# Combine the two datasets
-combined_data <- bind_rows(data2, data3)
+# Create
 
-avg_publish_years <- combined_data %>%
-  group_by(group) %>%
-  summarise(avg_publish_year = mean(publish_year, na.rm = TRUE))
+# Create a data frame for vertical lines
+vertical_lines <- data.frame(
+  rating_category = c("High-Rated", "Not High-Rated"),  # Match facet categories
+  line_year = c(2003, 2005)  # Years for vertical lines
+)
 
-# Create a combined scatter plot with facets
-ggplot(combined_data, aes(x = publish_year, y = rating)) +
-  geom_point() +
+# Create the faceted bar plot with vertical lines
+ggplot(data_combined, aes(x = as.factor(publish_year))) +
+  geom_bar(fill = "steelblue") +
+  geom_vline(
+    data = vertical_lines,
+    aes(xintercept = line_year),
+    color = "red",
+    linetype = "dashed",
+    size = 1,
+    inherit.aes = FALSE
+  ) +
+  labs(
+    title = "Number of Books by Publish Year and Rating Category",
+    x = "Publish Year",
+    y = "Number of Books"
+  ) +
+  facet_wrap(~rating_category, ncol = 1) +  # Facet by rating category
   theme_minimal() +
-  facet_wrap(~group, ncol = 1, scales = "free_y") +
-  geom_vline(data = avg_publish_years, aes(xintercept = avg_publish_year), 
-             color = "red", linetype = "dashed", size = 1) 
+  theme(
+    axis.text.x = element_text(angle = 90, hjust = 1)  # Tilt x-axis labels
+  )
+
 ```
-(CITATION) shows the relationship between a book's rating and the publish year.
+
+@fig-publish-year shows the relationship between a book's rating and the publish year.
 The horizontal axis shows the publish year, and vertical axis shows the rating of the book.
-The graph is split into two vertically, the top plot showing ratings of "high-rated" books and low-rated books.
-Low-rated books showed a higher concentration of publish year towards the right, suggesting a higher average publish year.
-By looking at the red line of fit (average publish year), "high-rated" books tend to be published before low-rated books.
+The graph is split into two vertically, the top plot showing ratings of high-rated books and low-rated books.
+It showed a left-tail distribution, peaking around the mid 2010s, followed by a big drop in late 2010s.
+High-rated books had a lower average publish year than low-rated books, at 2003 and 2005 respectively.
 
@@
 
-(FIGURE 5) shows the relationship between the rating of a book and the number of ratings it received.
-The red line indicates the cut-off for a book to be considered "highly-rated".
-It is apparent that books that are considered "highly_rated" (right of the red line) have far more ratings on average than low-rated books.
+@fig-rating-count shows the relationship between the rating of a book and the number of ratings it received.
+The red line indicates the cut-off for a book to be considered high-rated.
+It is apparent that books that are considered high_rated (right of the red line) have far more ratings on average than low-rated books.
 
@@
 
-This study employed a Bayesian logistic regression model to analyze the relationship between Children's book's "highly-rated" status and the characteristic of the book. The model is as follows:
+This study employed a Bayesian logistic regression model to analyze the relationship between children book's `high-rated` status and the characteristic of the book. The model is as follows:
 
@@
 
-The rstanarm package (CITATION) was used in order to run the regression model mentioned above.
-The default priors of the rstanarm package was used (CITATION).
+The rstanarm package [@citerstanarm] was used in order to run the regression model mentioned above.
+The default priors of the rstanarm package was used [@citerstanarm].
 These default priors are designed to be weakly informative, meaning they provide enough information to regularize the model and prevent extreme estimates, while being flexible to let the data drive the inference.
-By default, priors for regression coefficients are centered around 0 with a standard deviation of 2.5, which is shown in equations (Equation LIST).
+By default, priors for regression coefficients are centered around 0 with a standard deviation of 2.5, which is shown in equations \ref{eq3}, \ref{eq4}, \ref{eq5}, \ref{eq6}, \ref{eq7}, \ref{eq8}, \ref{eq9}, \ref{eq10}, \ref{eq11}.
 
@@
 
-The predictor variables shown in (LIST HERE) were chosen due to the number of studies regarding their influence on ratings of books.
-
-More specifically, I expect that
+The Bayesian logistic regression model was chosen because it is well-suited for binary outcome variables, making it appropriate for analyzing the likelihood of books being high-rated.
+Additionally, Bayesian methods enables the incorporation of prior knowledge and uncertainty into the analysis, which provides more robust estimates of the model parameters.
+[@citehannah]
 
@@
 
-After running the regression based on the model shown above, we get the coefficient values showcased in Table X (CITE HERE).
+After running the regression based on the model shown above, we get the coefficient values showcased in @tbl-book-model.
 
-COEFFICIENT RANGE (CITE) represent the 90% probability intervals of the estimates, where a coefficient is considered statistically significant if the range excludes 0.
-In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being "highly-rated" when positive and "low-rated" when negative.
+@fig-interval represent the 90% probability intervals of the estimates, where a coefficient is considered statistically significant if the range excludes 0.
+In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being high-rated when positive and low-rated when negative.
 
-With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being "highly-rated", assuming all else held constant, reflecting the analysis that was seen in DATA (CITE HERE).
-In contrast, the number of pages of a book, and the number of ratings no statistically significant influence on a book being "highly-rated".
+With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being `high-rated`, assuming all else held constant, reflecting the analysis that was seen in @sec-data.
+In contrast, the number of pages of a book, and the number of ratings no statistically significant influence on a the likelihood of a book being high-rated.
 
-Although the publish year was not statistically significant according to the GRAPH (CITE), it exhibited a slight negative relationship (coefficient: -0.01), consistent with previous findings (CITE) that "high-rated" books tend to have earlier publication years compared to "low-rated" ones.
+Although the publish year was not statistically significant according to the @fig-interval, it exhibited a slight negative relationship (coefficient: -0.01), consistent with previous findings @fig-publish-year that `high-rated` books tend to have earlier publication years compared to low-rated ones.
 
 ```{r}
-#| label: summary_statistic_cleaned_dataset3
+#| label: tbl-book-model
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
 #| echo: false
+#| warning: false
 
@@
 
-As shown by SECTIOM  (RESULTS), the number of ratings a book receives and its page length had no statistical significance on a book being highly-rated.
+As shown by @sec-result, the number of ratings a book receives and its page length had no statistical significance on a book being highly-rated.
 In particular, these factors are likely independent of how readers perceive its quality or enjoyment.
@@
 
-Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions (CITATION).
+Furthermore, the irrelevance of the number of ratings a book receives could be explained by herd effect; where readers rely on the ratings and reviews of others to make their own rating decisions [@citeherd].
 Therefore, once a book has many reviews, its average rating stabilizes, making the number of ratings irrelevant to the overall evaluation.
@@
 
-The results in SECTION (RESULTS), indicated a big positive relationship between book cover types and its "highly-rated" status.
-In particular, the "Kindle Edition" book cover had the highest coefficient (NUMBER HERE).
+The results in @sec-result, indicated a big positive relationship between book cover types and its high-rated status.
+In particular, the "Kindle Edition" book cover had the highest coefficient (4.239).
 A potential explanation could be that ebooks (such as Kindle Edition) are often preferred over physical books for their convenience, affordability and accessibility.
 Additionally ebooks are often cheaper due to saving material costs and saving physical space.
-In Middle-Eastern countries, 74.6% students preferred e-books in terms of easy to carry and 80.6% of them spent more time reading from e-books than printed books (CITATION HERE).
+In Middle-Eastern countries, 74.6% students preferred e-books in terms of easy to carry and 80.6% of them spent more time reading from e-books than printed books [@citepreference].
 Thus, it could appear that e-books have an advantage in attracting those seeking convenience and personalization in their reading, potentially explaining its big relationship compared to any other book cover types.
@@
 
-While the result in SECTION (RESULT) showed that the publish year was statistically insignificant, (GRAPH) a small negative correlation which was expected.
+While the result in @sec-result showed that the publish year was statistically insignificant, @fig-publish-year showed a small negative correlation.
 In particular, high-rated books had an older publish year than lowly-rated books.
@@
 
-We used a posterior predictive check in FIGURE (CITE) to evaluate how well the model fits the data.
-This compares the observed data Y (CHANGE) against the replicated data y-REP (CHANGE) which was generated by our model in SECTION 3 (CITE).
+We used a posterior predictive check in @fig-distribution to evaluate how well the model fits the data.
+This compares the observed data `y` against the replicated data \mbox{y$_i$} which was generated by our model in @sec-model.
 The posterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset4
+#| label: fig-distribution
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
 #| echo: false
+#| warning: false
 
@@
 
-In FIGURE BELOW (CITE) we compared the posterior with the prior, to examine how the estimates change once data is taken into account (CITE ALEXANDER).
+In @fig-post-prior we compared the posterior with the prior, to examine how the estimates change once data is taken into account (CITE ALEXANDER).
 Most of the variables do not vary even after data was taken into account, showing that the observed data matches the expectations of a "highly-rated" book.
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset5
+#| label: fig-post-prior
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
 #| echo: false
-
+#| warning: false
+#| 
 analysis_data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
+model_file <- readRDS(file = here::here("models/model.rds"))
 
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset6
+#| label: fig-trace
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
@@
 #| layout-ncol: 3
-
+#| warning: false
+#| 
 model_file <- readRDS(file = here::here("models/model.rds"))
@@
 
-FIGURE X AND Y are the trace plot of the model and Rhat plot of the model respectively.
-
+@fig-trace and @fig-rhat are the trace plot of the model and Rhat plot of the model respectively.
 The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model.
-
 Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 (CITE ALENXANDER)
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset7
+#| label: fig-rhat
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
 #| echo: false
+#| warning: false
 
+model_file <- readRDS(file = here::here("models/model.rds"))
 plot(model_file, "rhat")
@@
 ```{r}
-#| label: summary_statistic_cleaned_dataset72
+#| label: fig-interval
 #| fig-cap: "Summary Statistic of the Cleaned Dataset"
 #| echo: false
+#| warning: false
 
+model_file <- readRDS(file = here::here("models/model.rds"))
 modelplot(model_file, conf_level = 0.9, coef_omit = c(5,8)) +

### 2024-11-29 paper/paper.qmd
finished readme.md

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Children's Books"
+subtitle: "What factors influence the likelihood of a book being high-rated"
 author: 
@@
 date-format: long
-abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (CITATION).
+abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (Cookson 2020).
 By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating.
-The results showed that the book's cover type had the biggest positive impact on a book's rating.
-The insight from this research not only clarify the key elements that make high rated childrens' book so high-rated, but also enhance future authors to push the boundaries of their literature and writing choices."
+The results showed that the book's cover type had the biggest positive impact on the likelihood of a book being high-rated.
+The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
 format: pdf
@@
 A rating such as 4, in particular, suggests a strong endorsement without overstepping into exaggeration.
-Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being categorized as "highly-rated" (a score above 4)?
+Given this, a critical question arises; What factors of a book contribute to the likelihood of the book being categorized as "high-rated" (a score above 4)?
 
-In this paper, I analyzed how the characteristics of a book, such as cover type, page count, publish year, and rating counts affected the likelihood of a book being "highly-rated" using the Children's Book Ratings Data [@citedata].
+In this paper, I analyzed how the characteristics of a book, such as cover type, page count, publish year, and rating counts affected the likelihood of a book being "high-rated" using the Children's Book Ratings Data [@citedata].
 First, after data cleaning, I selected 9 variables on children book characteristics for my analysis in @sec-data.
@@
 
-The logistic regression model showed that book covers had the biggest influence on the likelihood of the book being high-rated, notably, the `Kindle Edition` type.
-The findings of this research have practical implications for the writing industry, to allow future generation authors to push the boundaries of literature.
+The logistic Bayesian logistic regression model revealed that book covers significantly influenced the likelihood of a book being rated highly, with the `Kindle Edition` format standing out as particularly impactful.
+These findings have practical implications for the publishing industry, offering valuable insights for authors and publishers to explore innovative ways to enhance reader engagement and elevate the literary experience.
 
-This research paper is structured as follows: @sec-data contains an overview of the dataset and some tables and graphs used to illustrate the variables employed in this analysis.
-@sec-model describes and justifies the logistic regression model that was produced in this report.
-@sec-result highlights the result of the model, @sec-discussion discusses some of the outcomes, weaknesses, and @sec-appendix contains additional information on model details.
+This research paper is structured as follows: @sec-data (Data) contains an overview of the dataset and some tables and graphs used to illustrate the variables employed in this analysis.
+@sec-model (Model) describes and justifies the logistic regression model that was produced in this report.
+@sec-result (Result) highlights the result of the model, @sec-discussion (Discussion) discusses some of the outcomes, weaknesses, and @sec-appendix (Appendix) contains additional information on model details.
 
@@
 The estimand of this paper is the probability that a children's book is "highly-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics.
-It is difficult to measure the exact number as there are millions of children's books that are published and not all of them will be accessed.
-For examples, children's books may have variations in ratings across countries.
-Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset [@sec-data].
+It is difficult to measure the exact number as there are millions of children's books that are published and there could be variations in ratings across countries.
+Therefore in this paper, we attempt to estimate the estimand using a logistic regression model which is fitted using a sample from the Children's Book Rating dataset [@citedata].
 
@@
 Cookson's dataset contained over 9,000 records of children's books that contained information of books such as title, author, ratings, publisher and more.
-In the initial step, data-cleaning was performed and relevant variables were selected.
+In the initial step, data cleaning was performed and relevant variables were selected.
 First, entries with missing information were filtered out, and variables that were irrelevant to this study were also removed, which included variables such as book title.
-Then, a new variable called "highly-rated" was created, which was a binary variable indicating if the book had a rating over 4 (1 if it exceeded 4, 0 else).
+Then, a new variable called `rated_high` was created, which was a binary variable indicating if the book had a rating over 4 (1 if it exceeded 4, 0 else).
 After cleaning and creating this new variable, there were 9240 entries in the cleaned dataset.
 
-Data analysis is performed using statistical programming language , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales].
+Data analysis is performed using Statistical Programming Language R [@citeR] , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales].
 
@@
 
-@tbl-cleaned-dataset-preview presents the first 5 rows from the cleaned dataset, which contains information on children's book.
+@tbl-cleaned-dataset-preview presents the first 5 rows from the cleaned dataset.
 
@@
 
-- `rated_high`: A binary variable telling us if a book is rated high or not (above a 4 rating)
+- `rated_high`: A binary variable telling us if a book is "high-rated" or not (above a 4 rating)
   - `0`: The book has a rating below 4
@@
 
-- `cover`: A categorical variable representing the type of the book, which can include:
+- `cover`: A categorical variable representing the cover type of the book, which can include:
   - `Ebook`: The book is in a digital format.
@@
 @tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset.
-It showed that books that were considered high-rated had more pages on average than low-rated books.
-Furthermore, high-rated books were on average published 2 years before low rated books, with publish year of 2005 and 2003 for the low-rated books and high-rated books respectively.
-High-rated books also received far more ratings on average at 8000 ratings, more than four times of low-rated books at an average of 2000 reviews per book.
-Lastly, Kindle covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books).
+It showed that books that were considered "high-rated" had more pages on average than "low-rated books".
+Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2005 and 2003 for the "low-rated" and "high-rated" books respectively.
+"High-rated" books also received far more ratings on average at 8,000 ratings, more than four times that of "low-rated" books at an average of 2000 reviews per book.
+Lastly, `Kindle Edition` covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books).
 These variables are key in the analysis, and are further mentioned in @sec-data.
@@
 #| warning: false
+
 summary_table <- data %>%
@@
 #| label: fig-most-common-covers
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Proportion of High-rated Books by Cover Type"
 #| echo: false
@@
 
+# find the proportion of books by cover type
+# (# of high-rated book / total # of high-rated books)
 cover_proportions <- data3 %>%
@@
   summarise(
-    total_books = n(),                                # Total number of books for each cover type
-    high_rated_books = sum(rated_high, na.rm = TRUE), # Total number of highly-rated books for each cover type
-    high_rated_pct = high_rated_books / total_books   # Proportion of highly-rated books
+    total_books = n(),                             
+    high_rated_books = sum(rated_high, na.rm = TRUE), 
+    high_rated_pct = high_rated_books / total_books  
   ) %>%
-  arrange(desc(high_rated_pct))  # Sort by the highest proportion
+  arrange(desc(high_rated_pct))  # Sort from highest
 
-# Create the bar plot
 ggplot(cover_proportions, aes(x = high_rated_pct, y = reorder(cover, high_rated_pct), fill = high_rated_pct)) +
@@
             hjust = -0.1, 
-            size = 3.5) +  # Add percentage labels
+            size = 3.5) +  
   labs(
-    title = "Proportion of Highly-Rated Books by Cover Type",
-    x = "Proportion of Highly-Rated Books",
+    x = "Proportion",
     y = "Cover Type"
   ) +
-  scale_x_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) + # Format x-axis as percentages
+  scale_x_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) + 
   theme_minimal() +
@@
 
-@fig-most-common-covers shows the proportion of `high-rated` books for each cover type.
-`Kindle Edition` books had the highest proportions of `high-rated` books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively.
-This illustrates that generally, digitally formatted books had higher proportions of `high-rated` books compared to physical formats.
+@fig-most-common-covers shows the proportion of "high-rated" books for each cover type.
+`Kindle Edition` books had the highest proportions of "high-rated" books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively.
+This illustrates that generally, digitally formatted books had higher proportions of "high-rated" books compared to physical formats.
 This finding also reflects the result from @tbl-summary-statistic.
@@
 #| label: fig-page-count
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Average Page Counts of High-rated and Low-rated Books"
 #| echo: false
@@
   labs(
-    title = "Average Pages by High Rated",
     x = "High Rated (1 = Yes, 0 = No)",
@@
 
-@fig-page-count shows that `high-rated` books have more page count than low-rated books.
+@fig-page-count shows that "high-rated" books have more page count than "low-rated" books.
 Highly-rated books had an average page count of 66.1, compared to the 57.6 average page count of low-rated books.
@@
 #| label: fig-publish-year
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Number of Books by Publish Year and Rating Status"
 #| echo: false
@@
   labs(
-    title = "Number of Books by Publish Year and Rating Category",
     x = "Publish Year",
@@
 #| label: fig-rating-count
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Rating Counts by the Rating of the Book"
 #| echo: false
@@
   geom_point() +
-  theme_minimal()
+  theme_minimal() +
+    labs(
+    x = "Rating",
+    y = "Number of Ratings"
+  ) 
 ```
@@
 @fig-rating-count shows the relationship between the rating of a book and the number of ratings it received.
-The red line indicates the cut-off for a book to be considered high-rated.
-It is apparent that books that are considered high_rated (right of the red line) have far more ratings on average than low-rated books.
+The red line indicates the cut-off for a book to be considered "high-rated".
+It is apparent that books that are considered "high_rated" (right of the red line) have far more ratings on average than "low-rated" books.
 
@@
 
-This study employed a Bayesian logistic regression model to analyze the relationship between children book's `high-rated` status and the characteristic of the book. The model is as follows:
+This study employed a Bayesian logistic regression model to analyze the relationship between children book's `rated_high`` status and the characteristic of the book. The model is as follows:
 
@@
 @fig-interval represent the 90% probability intervals of the estimates, where a coefficient is considered statistically significant if the range excludes 0.
-In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being high-rated when positive and low-rated when negative.
+In addition to this, these coefficients are expressed in log-odds, meaning it suggests a positive association with a book being high-rated when positive and low-rated when negative [@citehannah].
 
-With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being `high-rated`, assuming all else held constant, reflecting the analysis that was seen in @sec-data.
-In contrast, the number of pages of a book, and the number of ratings no statistically significant influence on a the likelihood of a book being high-rated.
+With this in mind, we can see that, the Kindle Edition cover type had the highest correlation with a book being "high-rated", assuming all else held constant, reflecting the analysis that was seen in @sec-data.
+In contrast, the number of pages of a book, and the number of ratings had no statistically significant influence on the likelihood of a book being "high-rated".
 
-Although the publish year was not statistically significant according to the @fig-interval, it exhibited a slight negative relationship (coefficient: -0.01), consistent with previous findings @fig-publish-year that `high-rated` books tend to have earlier publication years compared to low-rated ones.
+Although the publish year was not statistically significant according to the @fig-interval, it exhibited a slight negative relationship (coefficient -0.01), consistent with previous findings from @fig-publish-year that "high-rated" books tend to have earlier publication years compared to "low-rated" ones.
 
@@
 #| label: tbl-book-model
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| tbl-cap: "Modeling the likelihood of a book being High-rated"
 #| echo: false
@@
 
+# Code adapted from Alexander (2023)
 model_file <- readRDS(file = here::here("models/model.rds"))
@@
 
-As shown by @sec-result, the number of ratings a book receives and its page length had no statistical significance on a book being highly-rated.
+As shown by @sec-result, the number of ratings a book receives and its page length had no statistical significance on a book being "high-rated".
 In particular, these factors are likely independent of how readers perceive its quality or enjoyment.
@@
 
-The results in @sec-result, indicated a big positive relationship between book cover types and its high-rated status.
+The results in @sec-result, indicated a big positive relationship between book cover types and its `rated_high` status.
 In particular, the "Kindle Edition" book cover had the highest coefficient (4.239).
@@
 While the result in @sec-result showed that the publish year was statistically insignificant, @fig-publish-year showed a small negative correlation.
-In particular, high-rated books had an older publish year than lowly-rated books.
+In particular, "high-rated" books had an older publish year than "low-rated" books, and we observed with a left-tail distribution with a peak around the mid 2010s, followed by a sharp drop in the late 2010s.
 
@@
 
-The second explanation could be that older books may benefit from nostalgia, where readers could assign higher ratings due to a stronger emotional connection and cultural significance they hold.
+The reason for the sudden drop in the late 2010s could be explained by the COVID-19 pandemic, where lockdowns could have put more emphasis on other forms of entertainment such as Netflix, TV and more.
 
@@
 #| label: fig-distribution
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Posterior predictive check"
 #| echo: false
@@
 
-In @fig-post-prior we compared the posterior with the prior, to examine how the estimates change once data is taken into account (CITE ALEXANDER).
-Most of the variables do not vary even after data was taken into account, showing that the observed data matches the expectations of a "highly-rated" book.
+In @fig-post-prior we compared the posterior with the prior, to examine how the estimates change once data is taken into account [@citealexander].
+Most of the variables do not vary even after data was taken into account, showing that the observed data matches the expectations of a "high-rated" book.
 
@@
 #| label: fig-post-prior
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Comparison of the prior and posterior"
 #| echo: false
@@
 #| label: fig-trace
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Trace plot"
 #| echo: false
@@
 #| warning: false
-#| 
+
 model_file <- readRDS(file = here::here("models/model.rds"))
@@
 The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model.
-Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 (CITE ALENXANDER)
+Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 [@citealexander]
 
@@
 #| label: fig-rhat
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Rhat Plot"
 #| echo: false
@@
 #| label: fig-interval
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "90% Credibility Intervals for Predictors of High-rated Books"
 #| echo: false
@@
 
+\newpage
+
 # References

### 2024-11-29 scripts/02-data_cleaning.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Cleans the children'sbook data
+# Purpose: Cleans the children's book data
 # Author: Hyunje Park 
 # Date: November 26, 2024
 # Contact: hyunje.park@mail.utoronto.ca
@@ -24,4 +24,3 @@ data <- data %>% select(-c(title, publisher, author, isbn, original_publish_year
 
 #### Save data in parquet file ####
 write_parquet(data, "data/analysis_data/analysis_data.parquet") 
-

### 2024-11-29 scripts/04-model_data.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
+# Purpose: Models whether or not a book is high-rated based on book characteristics
 # Author: Hyunje Park
 # Date: November 26, 2024
 # Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites:
-
+# Pre-requisites: 02-data_cleaning.R
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-29 paper/paper.qmd
fixed alignment issues with references in pdf file

@@
 The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
-format: pdf
+format:
+  pdf:
+    fig.pos: "H"
 toc: true
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: tbl-cleaned-dataset-preview
@@
 
-```{r}
+```{r, fig.pos: "H"}
 #| message: false
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: tbl-summary-statistic
-#| fig-cap: "Summary Statistic of the Cleaned Dataset"
+#| fig-cap: "Summary Statistic of the Dataset"
 #| echo: false
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-most-common-covers
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-page-count
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-publish-year
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-rating-count
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: tbl-book-model
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-distribution
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-post-prior
@@
 
-```{r}
+\newpage
+
+```{r,  fig.pos: "H"}
 #| label: fig-trace
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-rhat
@@
 
-```{r}
+```{r,  fig.pos: "H"}
 #| label: fig-interval

### 2024-11-29 paper/paper.qmd
fixed pdf

@@
 title: "Children's Books"
-subtitle: "What factors influence the likelihood of a book being high-rated"
+subtitle: "What factors influence the likelihood of a book being high-rated?"
 author: 
@@
 data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
+
 ```
@@
 # cant fit it in one line, put it next
-second_half <- data %>% select(7:12)
+second_half <- data %>% select(7:11)
 
@@
 It showed that books that were considered "high-rated" had more pages on average than "low-rated books".
-Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2005 and 2003 for the "low-rated" and "high-rated" books respectively.
-"High-rated" books also received far more ratings on average at 8,000 ratings, more than four times that of "low-rated" books at an average of 2000 reviews per book.
+Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2002 and 2000 for the "low-rated" and "high-rated" books respectively.
+"High-rated" books also received far more ratings on average at 9,5092 ratings, more than four times that of "low-rated" books at an average of 2002 reviews per book.
 Lastly, `Kindle Edition` covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books).
@@
 @fig-most-common-covers shows the proportion of "high-rated" books for each cover type.
-`Kindle Edition` books had the highest proportions of "high-rated" books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively.
+`Kindle Edition` books had the highest proportions of "high-rated" books at 75%, followed by Paperback and Ebook, at 64% and 60.8% respectively.
 This illustrates that generally, digitally formatted books had higher proportions of "high-rated" books compared to physical formats.
@@
 @fig-page-count shows that "high-rated" books have more page count than "low-rated" books.
-Highly-rated books had an average page count of 66.1, compared to the 57.6 average page count of low-rated books.
+Highly-rated books had an average page count of 70.3, compared to the 66.9 average page count of low-rated books.
 
@@
 The graph is split into two vertically, the top plot showing ratings of high-rated books and low-rated books.
-It showed a left-tail distribution, peaking around the mid 2010s, followed by a big drop in late 2010s.
-High-rated books had a lower average publish year than low-rated books, at 2003 and 2005 respectively.
+It showed a left-tail distribution, peaking around the mid 2000s, followed by a big drop in late 2010s.
+High-rated books had a lower average publish year than low-rated books, at 2002 and 2000 respectively.
 

### 2024-11-29 scripts/02-data_cleaning.R

@@ -16,6 +16,10 @@ library(arrow)
 data <- read.delim("data/raw_data/childrens-books.txt", header = TRUE, sep = "\t")
 print(data)
 
+#remove any NA value entries
+data <- na.omit(data)
+
+
 # make a new column that determines if a book is high rated 
 data$"rated_high" <- ifelse(data$rating > 4, 1, 0)
 
@@ -24,3 +28,4 @@ data <- data %>% select(-c(title, publisher, author, isbn, original_publish_year
 
 #### Save data in parquet file ####
 write_parquet(data, "data/analysis_data/analysis_data.parquet") 
+

### 2024-11-29 scripts/01-simulate_data.R
finished simulate_data.r

@@ -11,42 +11,50 @@
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+library(lintr)
+library(styler)
 
+set.seed(529)
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
+n <- 4000
+sim_data <- data.frame(
+  cover = sample(c("Paperback", "Hardcover"), n, replace = TRUE, prob = c(0.6, 0.4)),
+  pages = sample(50:500, n, replace = TRUE),
+  publish_year = sample(1950:2020, n, replace = TRUE),
+  rating = round(runif(n, 1, 5), 2),
+  rating_count = sample(100:1000000, n, replace = TRUE),
+  rating_5 = sample(10:500000, n, replace = TRUE),
+  rating_4 = sample(10:300000, n, replace = TRUE),
+  rating_3 = sample(10:200000, n, replace = TRUE),
+  rating_2 = sample(10:100000, n, replace = TRUE),
+  rating_1 = sample(10:50000, n, replace = TRUE)
 )
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+# Tests and Validation
+# 1. Check data types and structure
+str(sim_data)
 
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
-  )
-)
+# 2. Summarize the dataset to check ranges and distributions
+summary(sim_data)
+
+# 3. Verify relationships between variables
+# Check that rating components add up
+sim_data <- sim_data %>%
+  mutate(total_ratings = rating_5 + rating_4 + rating_3 + rating_2 + rating_1)
+
+if (all(sim_data$total_ratings == sim_data$rating_count)) {
+  print("Rating components correctly sum to rating_count.")
+} else {
[…]

### 2024-11-29 scripts/02-data_cleaning.R

@@ -28,4 +28,5 @@ data <- data %>% select(-c(title, publisher, author, isbn, original_publish_year
 
 #### Save data in parquet file ####
 write_parquet(data, "data/analysis_data/analysis_data.parquet") 
+write_csv(data, "data/analysis_data/analysis_data.csv")
 

### 2024-11-29 scripts/01-simulate_data.R
finished test_analysis_data.r

@@ -5,9 +5,7 @@
 # Date: 26 September 2024
 # Contact: rohan.alexander@utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
+# Pre-requisites: Install the packages mentioned below
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-29 scripts/02-data_cleaning.R

@@ -26,7 +26,9 @@ data$"rated_high" <- ifelse(data$rating > 4, 1, 0)
 # drop unnecessary columns 
 data <- data %>% select(-c(title, publisher, author, isbn, original_publish_year))
 
-#### Save data in parquet file ####
+#### Save data in parquet file, used for paper.qmd ####
 write_parquet(data, "data/analysis_data/analysis_data.parquet") 
+
+# save as csv, for test_analysis_data.R
 write_csv(data, "data/analysis_data/analysis_data.csv")
 

### 2024-11-29 scripts/03-test_analysis_data.R

@@ -1,0 +1,53 @@
+#### Preamble ####
+# Purpose: Tests... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 26 September 2024 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+
+analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+
+#### Test data ####
+# Test that the dataset has 3965 rows - dataset contains this many rows
+test_that("dataset has 3965 rows", {
+  expect_equal(nrow(analysis_data), 3965)
+})
+
+# Test that the dataset has 11 columns
+test_that("dataset has 11 columns", {
+  expect_equal(ncol(analysis_data), 11)
+})
+
+# Test that the 'cover' column is character type
+test_that("'cover' is character", {
+  expect_type(analysis_data$cover, "character")
+})
+
+# Test that the 'pages' column is double type
+test_that("'pages' is character", {
+  expect_type(analysis_data$pages, "double")
+})
+
+# Test that the 'rating' column is double type
+test_that("'rating' is character", {
+  expect_type(analysis_data$rating, "double")
+})
+
+
+# Test that there are no missing values in the dataset
+test_that("no missing values in dataset", {
+  expect_true(all(!is.na(analysis_data)))
+})
+
+# Test that 'cover' contains only valid cover types
+valid_cover <- c("Paperback", "Hardcover", "Board Book", "Kindle Edition", "Ebook", "Audiobook")
+test_that("'cover' contains valid cover types", {
+  expect_true(all(analysis_data$cover %in% valid_cover))
+})

### 2024-11-29 scripts/05-exploratory_data_analysis.R
finished observations and coefficients

@@ -7,31 +7,36 @@
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
 
-
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(lintr)
+library(ggplot2)
+library(stylr)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
+model <- readRDS(here::here("models/model.rds"))
 
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# MAKE PLOTS 
+# Distribution of ratings
+ggplot(sim_data, aes(x = rating)) +
+  geom_histogram(binwidth = 0.1, fill = "blue", color = "white") +
+  theme_minimal() +
+  labs(title = "Distribution of Ratings", x = "Rating", y = "Count")
 
+# Distribution of pages
+ggplot(sim_data, aes(x = pages)) +
+  geom_histogram(binwidth = 10, fill = "green", color = "white") +
+  theme_minimal() +
+  labs(title = "Distribution of Pages", x = "Pages", y = "Count")
+
+# Distribution of rating counts
+ggplot(sim_data, aes(x = rating_count)) +
+  geom_histogram(binwidth = 50000, fill = "purple", color = "white") +
+  theme_minimal() +
+  labs(title = "Distribution of Rating Counts", x = "Rating Count", y = "Count")
 
 #### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
-
-
+lint(filename = here("scripts/05-exploratory_data_analysis.R"))
+style_file(path = here("scripts/05-exploratory_data_analysis.R"))

### 2024-11-29 scripts/07-test_observations_coefficient.R

@@ -1,0 +1,25 @@
+#### Preamble ####
+# Purpose: Replicated graphs from... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+model_file <- readRDS(file = here::here("models/model.rds"))
+
+#### Test Data ####
+
+# check the coefficients
+test_that("Check summary", {
+  summary_book <- summary(model_file)
+  expect_true("summary.stanreg" %in% class(summary_book))})
+
+# check that the number of observations are correct (9240)
+test_that("Check number of observations is correct", {
+  expect_equal(nrow(model_file$data), 9240)
+})

### 2024-11-29 scripts/02-data_cleaning.R
added lint and style to scripts

@@ -32,3 +32,6 @@ write_parquet(data, "data/analysis_data/analysis_data.parquet")
 # save as csv, for test_analysis_data.R
 write_csv(data, "data/analysis_data/analysis_data.csv")
 
+# lint and style the code
+lint(filename = here::here("scripts/02-data_cleaning.R"))
+style_file(path = here::here("scripts/02-data_cleaning.R"))

### 2024-11-29 scripts/04-model_data.R

@@ -4,11 +4,13 @@
 # Date: November 26, 2024
 # Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 02-data_cleaning.R
+# Pre-requisites: Run 02-data_cleaning.R for the parquet file
 
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(lintr)
+library(styler)
 
 #### Read data ####
 analysis_data <- read_parquet("data/analysis_data/analysis_data.parquet")
@@ -35,4 +37,6 @@ saveRDS(
   file = "models/model.rds"
 )
 
-
+# lint and style the code
+lint(filename = here::here("scripts/04-model_data.R"))
+style_file(path = here::here("scripts/04-model_data.R"))

### 2024-11-29 scripts/06-test_observations_coefficient.R

@@ -1,10 +1,10 @@
 #### Preamble ####
-# Purpose: Replicated graphs from... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the number of observations and tests the model coefficient from 04-model_data.R
+# Author: Hyunje Park
+# Date: 29 November 2024 
+# Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
+# Pre-requisites: Run 04-model_data.R to get the model
 
 
 #### Workspace setup ####
@@ -23,3 +23,7 @@ test_that("Check summary", {
 test_that("Check number of observations is correct", {
   expect_equal(nrow(model_file$data), 9240)
 })
+
+# lint and style the code
+lint(filename = here::here("scripts/06-test_observations_coefficient.R"))
+style_file(path = here::here("scripts/06-test_observations_coefficient.R"))

### 2024-11-29 scripts/01-simulate_data.R
fixed preamble for all the scripts

@@ -1,9 +1,8 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates the Children's Book Data
+# Author: Hyunje Park
+# Date: 29 November 2024
+# Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: Install the packages mentioned below
 

### 2024-11-29 scripts/02-data_cleaning.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Cleans the children's book data
+# Purpose: Cleans the Children's book data
 # Author: Hyunje Park 
 # Date: November 26, 2024
 # Contact: hyunje.park@mail.utoronto.ca
@@ -11,6 +11,8 @@ library(tidyverse)
 library(dplyr)
 library(readr)
 library(arrow)
+library(lintr)
+library(styler)
 
 #### Clean data ####
 data <- read.delim("data/raw_data/childrens-books.txt", header = TRUE, sep = "\t")

### 2024-11-29 scripts/03-test_analysis_data.R

@@ -1,16 +1,17 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the cleaned Children's book data
+# Author: Hyunje Park
+# Date: November 29 2024
+# Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Run 02-data_cleaning.R to get the cleaned data
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(testthat)
+library(lintr)
+library(styler)
 
 analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
 

### 2024-11-29 scripts/05-exploratory_data_analysis.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Explores and understands the dataset and model by creating visualizations
+# Author: Hyunje Park
+# Date: 29 November 2024
+# Contact: hyunje.park@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Run 02-data_cleaning.R and 04-model_data.R 
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-29 scripts/06-test_observations_coefficient.R

@@ -9,6 +9,8 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(lintr)
+library(styler)
 library(testthat)
 model_file <- readRDS(file = here::here("models/model.rds"))
 

### 2024-11-29 paper/paper.qmd
finished observations and coefficients
added citation for lintr and styler

@@
 library(scales)
+library(testthat)
+library(lintr)
+library(styler)
 
@@
 
-Data analysis is performed using Statistical Programming Language R [@citeR] , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales].
+Data analysis is performed using Statistical Programming Language R [@citeR] , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales] and `testthat` [@testthat].
+The code involved in the analysis was styled using `lintr` [@citelintr] and `styler` [@citestyler].
 
@@
   theme(legend.position = "bottom")
+
 ```

### 2024-11-29 scripts/01-simulate_data.R

@@ -52,6 +52,6 @@ print("Cover Proportions:")
 print(cover_proportions)
 
 
-#### lint and style the code nicely ####
+#### lint and style the code ####
 lint(filename = here('scripts/00-simulate_data.R'))
 style_file(path = here("scripts/00-simulate_data.R"))

### 2024-11-30 paper/paper.qmd
final typo checks

@@
 ---
-title: "Children's Books"
+title: "Children's Books:"
 subtitle: "What factors influence the likelihood of a book being high-rated?"
@@
 
-The logistic Bayesian logistic regression model revealed that book covers significantly influenced the likelihood of a book being rated highly, with the `Kindle Edition` format standing out as particularly impactful.
+The Bayesian logistic regression model revealed that book covers significantly influenced the likelihood of a book being high-rated, with the `Kindle Edition` format standing out as particularly impactful.
 These findings have practical implications for the publishing industry, offering valuable insights for authors and publishers to explore innovative ways to enhance reader engagement and elevate the literary experience.
@@
 
-The estimand of this paper is the probability that a children's book is "highly-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics.
+The estimand of this paper is the probability that a children's book is "high-rated" (has a rating over 4 on a 0-5 scale), based on book characteristics.
 It is difficult to measure the exact number as there are millions of children's books that are published and there could be variations in ratings across countries.
@@
 
-Data analysis is performed using Statistical Programming Language R [@citeR] , along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales] and `testthat` [@testthat].
+Data analysis is performed using Statistical Programming Language R [@citeR], along with packages `tidyverse` [@citetidyverse], `palmerpenguins` [@citepalmerpenguins], `kableExtra` [@citekableextra], `arrow` [@citearrow], `readr` [@citereadr], `rstanarm` [@citerstanarm], `modelsummary` [@citemodelsummary], `dplyr` [@citedplyr], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `scales` [@citescales] and `testthat` [@citetestthat].
 The code involved in the analysis was styled using `lintr` [@citelintr] and `styler` [@citestyler].
@@
 @tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset.
-It showed that books that were considered "high-rated" had more pages on average than "low-rated books".
+It showed that books that were considered "high-rated" had more pages on average than "low-rated" books.
 Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2002 and 2000 for the "low-rated" and "high-rated" books respectively.
-"High-rated" books also received far more ratings on average at 9,5092 ratings, more than four times that of "low-rated" books at an average of 2002 reviews per book.
-Lastly, `Kindle Edition` covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books).
+"High-rated" books also received far more ratings on average at 9,592 ratings, more than four times that of "low-rated" books at an average of 2002 reviews per book.
+Lastly, `Kindle Edition` covers had the highest proportion of "high-rated" books out of any other cover types (as well as low-rated books).
 These variables are key in the analysis, and are further mentioned in @sec-data.
@@
 @fig-page-count shows that "high-rated" books have more page count than "low-rated" books.
-Highly-rated books had an average page count of 70.3, compared to the 66.9 average page count of low-rated books.
+High-rated books had an average page count of 70.3, compared to the 66.9 average page count of low-rated books.
 
@@
 
-This study employed a Bayesian logistic regression model to analyze the relationship between children book's `rated_high`` status and the characteristic of the book. The model is as follows:
+This study employed a Bayesian logistic regression model to analyze the relationship between children book's `rated_high` status and the characteristic of the book. The model is as follows:
 
@@
 We used a posterior predictive check in @fig-distribution to evaluate how well the model fits the data.
-This compares the observed data `y` against the replicated data \mbox{y$_i$} which was generated by our model in @sec-model.
+This compares the observed data `y` against the replicated data \mbox{y$_rep$} which was generated by our model in @sec-model.
 The posterior distribution fitting perfectly suggests that the Bayesian logistic regression model is a good model fit.
@@
 The trace plot shows oscillating horizontal lines, with overlaps between chains, showing no signs of issues with the model.
-Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 [@citealexander]
+Similarly, the Rhat plot doesn't indicate any issues with the model, as all the values remain close to 1 [@citealexander].
 
